---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# photon

<!-- badges: start -->
[![R-CMD-check](https://github.com/JsLth/photon/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JsLth/photon/actions/workflows/R-CMD-check.yaml)
[![R-hub](https://github.com/jslth/photon/actions/workflows/rhub.yaml/badge.svg)](https://github.com/jslth/photon/actions/workflows/rhub.yaml)
[![CRAN
status](https://www.r-pkg.org/badges/version/photon)](https://CRAN.R-project.org/package=photon)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Codecov test
coverage](https://codecov.io/gh/JsLth/photon/branch/main/graph/badge.svg)](https://app.codecov.io/gh/JsLth/photon?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/jslth/photon/badge/main)](https://www.codefactor.io/repository/github/jslth/photon/overview/main)
<!-- badges: end -->

`{photon}` is a simple interface and setup manager of the [photon](https://photon.komoot.io) OpenStreetMap geocoder. It features unstructured, structured, and reverse geocoding. The package allows requests to the public API but shines at setting up local instances to enable high-performance offline geocoding.

## Installation

To install the package from CRAN:

``` r
install.packages("photon")
```

You can install the development version of photon from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jslth/photon")
```

## Usage

When loading `{photon}`, the package assumes that you want send geocoding requests to the public photon API. If you want to change this, you can use the workhorse function `new_photon()`. Otherwise, you can directly start geocoding.

```{r geocode}
library(photon)
places <- c("Paris", "Shenzen", "Sao Paulo", "Kinshasa")

cities1 <- geocode(places, layer = "city")
cities1
```

Structured geocoding means providing address / place details in a structured format.

```{r}
places_str <- data.frame(
  city = places,
  countrycode = c("FR", "CN", "BR", "CD")
)
cities2 <- structured(places_str)
cities2
```

Reverse geocoding means taking point geometries and returning their addresses or place names.

```{r reverse}
cities3 <- reverse(cities1$geometry, layer = "city")
cities3
```

```{r compare}
all.equal(cities1, cities3)
```



## Offline geocoding

`{photon}` is designed to facilitate offline geocoding. `new_photon()` can install photon locally. The following code would install and start photon covering the country of Germany in the current working directory.

```{r offline, eval=FALSE}
photon <- new_photon(path = "./photon", region = "Germany")
photon$start()
```


## Related packages

- The [`{photon}`](https://github.com/rCarto/photon) package by Timothée Giraud interfaces photon but does not allow the setup of local instances and was abandoned a while ago.
- The [`{revgeo}`](https://CRAN.R-project.org/package=revgeo) package by Michael Hudecheck implements reverse geocoding using (among others) photon.
- The [`{tidygeocoder}`](https://jessecambon.github.io/tidygeocoder/) and [`{nominatimlite}`](https://dieghernan.github.io/nominatimlite/) packages implement general (OSM) geocoding using web APIs.
